\section{Experience}
\begin{entrylist}
\entry
    {2023--2025}
    {Elsevier}
    {Cambridge, UK}
    {\jobtitle{Director, Professional Services and Data Science}\\
    Led global Professional Services and Data Science (DSPS) delivering bespoke drug-development solutions using SciBite tech and AI. Scoped and designed complex solutions, supported pre-sales with scientific/technical insights, and guided value- and tech-focused partnerships; managed end-to-end engagements from target identification and clinical-trial analytics to post-market surveillance, coordinating SaaS and on-prem onboarding. Drove GenAI/LLM-driven R\&D, delivering commercialized features and contributing to senior leadership strategy. Notable outcomes include building and mentoring a 14+ person team (8 data scientists/consultants, 5 PMs); six PoCs with ≥75\% conversion; five service projects expanding key accounts and renewals; and six global conference appearances impacting pharma, life sciences, and clinical sectors.}
%------------------------------------------------
\entry
  {2021--2023}
  {SciBite, an Elsevier Company}
  {Cambridge, UK}
  {\jobtitle{Director Professional Services}\\
  Built and led a global team of technical consultants whose responsibilities involved scoping projects for prospective customers and providing expert advisory support to licensed customers. Overall remit of team was to drive the global expansion of SciBite products. As part of this role I also led efforts within the Customer Success space, defining and implementing key processes to enhance customer experience and retention.} 
%------------------------------------------------
\entry
  {2020--2021}
  {SciBite Ltd}
  {Cambridge, UK}
  {\jobtitle{Lead Technical Consultant}\\
  Led a team of Technical Consultants to drive increased adoption of SciBite technology in existing accounts through proactive technical advice and guidance. Worked closely with customers to understand their needs, gathering and sharing insights internally to influence product roadmaps and R\&D innovation.}
%------------------------------------------------
%------------------------------------------------
\end{entrylist}